S-Tipping vs B-Tipping

### 2018-04-20 paper/paper.Rmd
started jotting down eqns

address:
  - code: Some Institute of Technology
    address: Department of Environmental Science, Policy, and Management, University of California, Berkeley, CA 94720
  - code: epa
    address: Environmental Protection Agency, ...
abstract: |
  This is the abstract.

@@

Dimensionality reduction

>>>>

address:
  - code: espm
    address: Department of Environmental Science, Policy, and Management, University of California, Berkeley, CA 94720
  - code: epa
    address: Environmental Protection Agency, ...
abstract: |
  This is the abstract.

@@

Variable | Description
-------- | ----------------
 $A$     | Adult Bass
 $J$     | Juvenile Bass
 $F$     | Planktivore zooplankton
 $H$     | Herbivorous zooplankton
 $P$     | Phytoplankton

The original model presented in @Carpenter2008 is defined in terms of continuous dynamics within years coupled to discrete annual dynamics.  Within a given year:

$$\frac{d A}{dt} = - q E A$$
$$d F = \left(D_f (F_R - F) - c_{FA} FA \right) dt  + \sigma_F dW_f$$

$$ \frac{dJ}{dt} = -c_{JA} JA - \frac{c_{JF} v FJ}{h + v + c_{JF} F}$$

While dynamics between years are defined in terms of integrals over the within-year dynamics:

$$A_{t+1} = s \int_t^{t+i} \left(A_{t} + J_{t} \right) dt $$
$$F_{t+1} = \int_t^{t+i} F_{t} dt $$

$$J_{t+1} = fsA_{t+1}$$

Based on these equations, we can approximate these dynamics in continuous time as:

$$\frac{d A}{dt} = - q E A_t + sJ $$
$$d F = \left(D_f (F_R - F) - c_{FA} FA \right) dt  + \sigma_F dW_f$$

$$\frac{dJ}{dt} = -c_{JA} JA - \frac{c_{JF} v FJ}{h + v + c_{JF} F} + fA$$

Dynamics for herbivorous plankton and phytoplankton are given only in continuous time:

$$dH = \left(D_H (H_R - H) + \alpha c_{HP} HP - c_{HF} HF\right) dt + \sigma_H dW_h$$

$$dP = \left( r_P L \gamma(I_o, P) P  - m P - c_{PH} HP \right) dt + \sigma_P dW_P$$

### Non-Dimensionalization

$$\tilde F := D_f (F - F_R) $$
$$\frac{d A}{dt} = - q E A_t + sJ $$
$$d \tilde F = \left(-\tilde F - c_{fA} \tilde F A \right) dt  + \sigma_F dW_f$$
$$\alpha := \frac{h+v}{c_{JF}} $$

$$\frac{d J}{dt} = fA -\left(c_{JA} A + \frac{v F}{\alpha + F} \right) J $$

$$\tilde H = D_H (H - H_R) $$
$$d \tilde H = \tilde H \left(1 + \alpha c_{\tilde HP} P - c_{\tilde HF} F\right) dt + \sigma_H dW_h$$

### Dimensionality reduction
